\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{lipsum}
\graphicspath{ {images/} }
\begin{document}

\begin{titlepage}

\begin{center}
\begin{huge}
Swarm Visualiser - COS 301 Main Project
\\
Testing Specifications
\begin{small}
\\
Team: Dragon Brain
\\
Members:
\\
Matheu Botha u14284104
\\
Renton McInytre u14312710
\\
Emilio Singh u14006512
\\
Gerard van Wyk u14101263

\end{small}

\end{huge}
\end{center}
\end{titlepage}

\pagebreak

\tableofcontents

\section{Frameworks and Mechanisms}
\section{Frameworks and Mechanisms}
For our project, we are making use of Google Tests, a cross-platform Unit Testing library for C++. This is largely because our chosen standardised IDE, Jetbrains CLion has integrated support for the framework.

\section{Testing Strategies}
\subsection{Unit Tests}
Our project's unit tests work primarily based on Assert-like mechanisms for Google Test, wherein we generate objects with particular data and assure that values are as they should be, and ensuring invalid states are properly detected. These are done using the Google Test macros "EXPECT_EQ" (tests equality), "EXPECT_TRUE", "EXPECT_FALSE", "EXPECT_NE" (tests for inequality) and so on.
\newline Each test is defined within a TEST macro and can be run either individually or all together, via CLion. 




\section{Integration Tests}
\paragraph{•}
This section of the testing manual will contain all of the necessary details pertaining to the area of Integration Tests, and Integration Testing, as per project requirements and project dictates.
\subsection{Integration Requirements}
\paragraph{•}
In terms specifying the Integration Requirements for the project, we identify Program Modules. These Modules are separate components that will each provide services and possibly make use of other services from other Modules. As an integration challenge, the task is to ensure that all of these Modules are able to realise their service contracts and do not contribute to the failure of service contracts of other Modules.

The Modules are:
\begin{itemize}
\item Graphics Pipeline:
\item General Optimiser:
\item User Interface:
\item Manager:
\end{itemize}
 
\subsection{Integration Areas}
\subsection{Strategies}

\section{Areas of Concern}
\subsection{Key Points of Failure}
\lipsu

\section{Example Unit Test}

\end{document}
